A Toolbox for Manipulating and Assessing Color Palettes for Statistical Graphics

### 2019-02-26 pkg/colorspace/paper/Toolbox/article.Rmd
added more references to other color-related packages -> more intro/discussion still needed (marked with FIXME)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@460 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

@@

## Approximating palettes from other packages

@@

>>>>

FIXME: More comparison with/discussion of other palette packages.
the viridis palettes of @color:Smith+VanDerWalt:2015 developed for \pkg{matplotlib},
as provided by \proglang{R} package \pkg{viridis} [@color:viridis], and
the scientific color maps of @color:Crameri:2018 as provided by \proglang{R}
package \pkg{scico} [@color:scico]. All yield mostly well-balanced color palettes
and can be approximated reasonably well in \pkg{colorspace}
(see Section\ \ref{sec:approximations}).
A broad range of packages that provide color palettes that are "in harmony" as
they are extracted and clustered from movies, paintings, etc. However, many of these
are not so suitable for scientific visualization as they are not clearly 
qualitative/sequential/diverging. An influential package following such an
approach is \pkg{weanderson} [@color:wesanderson]. The \pkg{paletteer}
[@color:paletteer] package aggregates these and provides them in a unified
user interface.
Aims of code in \pkg{colorspace} are general trajectories, adaptable HCL
coordinates, along with visualization and assessment of palettes (beyond
color swatches).

@@

## Approximating palettes from other packages {#sec:approximations}

@@

FIXME: Discuss relation ship to other packages:

* \pkg{Polychrome} [@color:Polychrome]: qualitative palettes with more "categories".
* \pkg{roloc} [@color:roloc]: naming palettes.
* \pkg{colorscience} [@color:colorscience]: More color mappings.
* \pkg{paletteer} [@color:paletteer]: Aggregation of palettes.
